### 2021-09-03 chapters/testing/reproducibility.tex
add : docker vs vm machines

\section{Reproducibility}

@@

% The importance of Virtualisation for reproducibility \cite{howe_virtual_2012}
% some of the most important parts are
% - fewer constraints on research methods
% - on-demand backups
% - virtual Machines as Publications
% - more Variables captured

@@

\subsection{Dockerisation}
another solution would be using something that allows us to have the isolation from the host os and the ease of replication that virtual machines offer, and the direct interaction with the hardware that the classical method give.

One interessting solution would be using containers.

\subsection{Testing Protocol}
the results of this protocil can be found in the project of the continious integrtation that was made by the intern MAMADou to give a feedback about the evolution of the energyconsumption within time

>>>>

\section{Empirical Evaluation Protocol}

This thesis is based on the empirical analyses to measure the energy consumption. As we mentioned earlier, we have chosen the \emph{agile} methode. so basically we will reduce the energy consumption with trial and error.

@@

% The importance of Virtualisation for reproducibility \cite{howe_virtual_2012}
% some of the most important parts are
% - fewer constraints on research methods
% - on-demand backups
% - virtual Machines as Publications
% - more Variables captured
\subsection{Threats and Challenges}

@@

\begin{figure}
    \center{\includegraphics[width=1\linewidth]{imgs/virtualization_techniques}}
    \caption{Different Methods of Virtualzation}\label{reproducibility:virtualization_technique}
\end{figure}

\subsection{Containers}

another solution would be using something that allows us to have the isolation from the host os and the ease of replication that virtual machines offer, and the direct interaction with the hardware that the classical method give.
contarization offers a such advantages while keeping the isolation and the ease of replication for application.

Figure \ref{reproducibility:virtualization_technique} explains the differents in architecture between the clasic types2 of Virtualisation and Containers.
\begin{itemize}
    \item Type 1: runs directly on the hardware, it is mainly used by the cloud providers where there is no main OS, but just virtaul machines, we can site for this the open-srouce XEN and VMware ESX
    \item Type 2: runs over the hostmachine Operating System, mostly used for personal comptuers, VMware server and virtualBox are famous examples of this type, most of the reaserchers expermentation are run witht this type, howerver due to the 2 Operatings syestms the applications tend to be more slower
    \item containers : Instead of its own kernel, containers used the hots kernel to run their Os, which makes them ligher, quickers and use the full pontial use of the hardware. For this we can cite \emph{Docker}, \emph{Linux LXC}\emph{LXD} \cite{abuabdo_virtualization_2019}
\end{itemize}
\note{Rephrase so i include it before VMs+ add links to the technologies }

\subsection{Docker vs Virtual Machine}
Depsite that Type 1 is more performant than type 2, the second one is the most used in reaserch, since most researchers conducts their experements in their own machine. In the other hand, docker is the most famous thechonology for for containers,

%%%%% THINGS TO ADD : 
% the impact of docker on the reprodudicibility 
% Limits of docker 
% The docker files and the clarification of the methodology

\subsection{Docker and energy}
%  basically just rephrase the paper

\subsection{docker and accuracy}

\subsection{Testing Protocol}
the results of this protocil can be found in the project of the continious integrtation that was made by the intern Mamadou to give a feedback about the evolution of the energyconsumption within time

### 2021-09-03 chapters/testing/testing.tex
add : docker vs vm machines

\newpage
\chapter{Testing}
\label{chapter:testing}

In order to optimize the energy consumption of software we first want to setup a testing enviroment. This chapter will be dedicated to provide a set of guidelines to provide a \em{reproducible, accurate} and \em{representative} tests.
Each aspect will be detailed in the sections below

>>>>

\newpage

\chapter{Testing}
\label{chapter:testing}

In order to optimize the energy consumption of software we first want to setup a experemental enviroment. This chapter will be dedicated to provide a set of guidelines to provide a \em{reproducible, accurate} and \em{representative} tests.
Each aspect will be detailed in the sections below.
